Timeliness of security updates for Android

### 2014-07-30 security_scoring.tex
Fill out security scoring section and discuss the tables

There are several components to take into account:
\begin{description}
  \item[$i$] The proportion of the time were devices exposed to known vulnerabilities. This is equivalent to the BWE score \cite{TODO}
  \item[$u$] The proportion of devices run the latest version of Android shipped to any device produced by that manufacturer. This is a measure of internal updatedness, a low score would mean many devices are being left behind.
  \item[$m$] The mean number of outstanding vulnerabilities affecting devices not fixed on any device shipped by the manufacturer. This is related to the ??? measure \cite{TODO}
\end{description}
\begin{equation}
\mathrm{score} = (1 - i)\times 4 + u \times 3 + \frac{2}{1+e^m} \times 3
\end{equation}

>>>>

This score is computed from several components:
\begin{description}
  \item[$i$] The proportion of the time were devices exposed to known vulnerabilities. This is equivalent to Acer and Jackson's proposal~\cite{Acer2010} to measure the security based on the proportion of users with at least one unpatched critical vulnerability and is also $1 -$ the Vulnerability Free Days score~\cite{Wright2014}.
  \item[$u$] The proportion of devices run the latest version of Android shipped to any device produced by that manufacturer. This is a measure of internal updatedness, a low score would mean many devices are being left behind.
  \item[$m$] The mean number of outstanding vulnerabilities affecting devices not fixed on any device shipped by the manufacturer. This is related to the Median Active Vulnerabilities measure~\cite{Wright2014} but is the mean rather than the median.
%TODO should we compute the median instead?
\end{description}
\begin{equation}
\mathrm{score} = (1 - i)\times 4 + u \times 3 + \frac{2}{1+e^m} \times 3
\end{equation}

The scores accross the whole of android are that \daMeanInsecurityPerc\ of devices are exposed to known root exploits.
There are on average \daMeanOutstandingVulnerabilities\ outstanding vulnerabilities not fixed on any device.
Only on average \daUpdatednessPerc\ of devices run the most recent version of Android.
This gives a security score of \daSecurityScore/10.
\daTabSecScoressummary
However there are a wide variety of scores depending on the source of the device.
There have been many reports that Google's Nexus devices are better at getting updates than other Android devices because Google makes the original updates and ships them to its devices.
Table~\ref{tab:sec_summary} shows that this is the case with Nexus devices getting much better scores than non-Nexus devices.
\daTabSecScoresmanufacturer
Different manufacturers have very different scores, Table~\ref{tab:sec_manufacturer} shows the scores for the \daNumSigManufacturers\ manufacturers with a significant presence in our data.
Manufacturers are considered significant if we have data from at least \daSigNumDevices\ devices and at least \daSigNumDays\ days of contributions.
\daTabSecScoresmodel
Even within manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric.
